Computing Graphical Perception

### 2018-03-14 PAPER/01_related_work.tex

\section{Related Work}

\cite{cleveland_mcgill} Clevenland McGill experiments

@@

Pineo et al.~\cite{Pineo2012_computational_perception} present a method to automatically evaluating and optimizing visualizations using a computational model of human vision, based on a neural network simulation of the early perceptual processing in the retina and primary visual cortex. [JT] Copied from their abstract.

>>>>

\section{Previous Work}

\textbf{Graphical Perception.} Cleveland and McGill~\cite{cleveland_mcgill} introduced the concept of \emph{graphical perception} and investigated how different visual attributes and encodings are perceivable by humans. They define \emph{elementary perceptual tasks} as mental-visual stimuli to understand encodings in visualizations.

\cite{HeerBostock2010} Heer and Bostock, CHI 2010 --- Crowdsourcing Graphical Perception: Using Mechanical Turk to Assess Visualization Design

@@

\textbf{Visual Cortex Inspired Machine Learning.} LeNet etc and work from THomas Serre

\textbf{Computing Perception.}

Pineo et al.~\cite{Pineo2012_computational_perception} present a method to automatically evaluate and optimize visualizations using a computational model of human vision, based on a neural network simulation of the early perceptual processing in the retina and primary visual cortex. [JT] Copied from their abstract.
